Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2021-09-14 AttackTolerance/preprint/source/preprint.tex
Move AttackTolerance to subfolder.

\documentclass{sig-alternate-05-2015}

\usepackage[utf8]{inputenc}
\usepackage{afterpage}
\usepackage{epigraph}
\usepackage{tikz}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\usepackage{pifont} % http://ctan.org/pkg/pifont
\usepackage{float}

@@

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{}

% ISBN
\isbn{}

%Conference
\conferenceinfo{Pre-print}{Currently under peer review.}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Edward L. Platt \\
\affaddr{University of Michigan}\\
\email{elplatt@umich.edu}
\alignauthor
Daniel M. Romero \\
\affaddr{University of Michigan}\\
\email{drom@umich.edu}
}
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{1932 Wallamaloo Lane}\\
%       \affaddr{Wallamaloo, New Zealand}\\
%       \email{trovato@corporation.com}
% 2nd. author
%\alignauthor
%G.K.M. Tobin\titlenote{The secretary disavows
%any knowledge of this author's actions.}\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{P.O. Box 1212}\\
%       \affaddr{Dublin, Ohio 43017-6221}\\
%       \email{webmaster@marysville-ohio.com}
% 3rd. author

@@

@@

\begin{figure}[H]
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
A small increase in the number of utilized paths (network traffic)
can compensate for a large increase in attacker power.
}
\label{fig:pfail}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=4in,height=2.78in]{fig-partial-trust.pdf}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em bounded trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $s$) and receiver (Bob, $t$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can achieve the same level of attack-tolerance
as if they were directly connected by $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[height=3in]{fig-bf-route}
\end{center}
\caption{
A 3-dimensional wrap-around butterfly network.
Note that the rightmost nodes are the same nodes as the leftmost,
drawn twice for visual clarity.
The highlighted nodes and edges show the path from node (0,000)
to node (1,101).
\label{fig:bf-route}
}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics{fig-diameter}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The original network fragments when the top 1\% of nodes are removed.
With only 10\% of the butterfly edges present,
this value doubles to 2\%.
With 90\% of the edges rewired,
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The rewiring scheme does not require adding any additional edges.
}
\label{fig:diameter}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=5in,height=5in]{fig-mincut}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The effective redundancy is shown for several values of trust transitivity $h$.
For $h>0$, the original network has higher effective redundancy up to a crossover point,
after which the rewired network performs better.
}
\label{fig:mincut}
\end{figure}

@@

\begin{figure}[H]

@@

\begin{figure}[H]
\begin{center}
\includegraphics{fig-routing}
\end{center}
\caption{
An example of one path as constructed by the proposed multipath
routing algorithm.
The path is shown for $s = 10_2$
and $w = (6, 0110111_2)$.
\label{fig:routing}
}
\end{figure}

@@

\section*{Acknowledgments}
The authors would like to thank Tony Garnock-Jones, A. Frederick Dudley, and
Nathaniel Bezanson for helpful conversations.
This research was partly supported by the National Science Foundation under Grant No. IIS-1617820.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%
\end{document}

>>>>

\documentclass[twocolumn]{article}

\usepackage[top=0.75in,left=0.75in,right=0.75in,bottom=1in]{geometry}
\setlength{\columnsep}{0.33in}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{epigraph}
\usepackage[utf8]{inputenc}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\usepackage{pifont} % http://ctan.org/pkg/pifont
\usepackage{amsthm}
\usepackage{float}

@@

\title{Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network}
\author{
Edward L. Platt \\
University of Michigan\\
elplatt@umich.edu
\and
Daniel M. Romero \\
University of Michigan\\
drom@umich.edu
}
\date{}

@@

\noindent{\bf Keywords:}
Butterfly Topology,
Fault Tolerance,
Adversarial Faults,
Multipath Routing,
Censorship,
Decentralization.

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=3in]{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
A small increase in the number of utilized paths (network traffic)
can compensate for a large increase in attacker power.
}
\label{fig:pfail}
\end{figure}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=3in]{fig-partial-trust.pdf}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em bounded trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $s$) and receiver (Bob, $t$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can achieve the same level of attack-tolerance
as if they were directly connected by $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=2.5in]{fig-bf-route}
\end{center}
\caption{
A 3-dimensional wrap-around butterfly network.
Note that the rightmost nodes are the same nodes as the leftmost,
drawn twice for visual clarity.
The highlighted nodes and edges show the path from node (0,000)
to node (1,101).
\label{fig:bf-route}
}
\end{figure}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=3in]{fig-diameter}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The original network fragments when the top 1\% of nodes are removed.
With only 10\% of the butterfly edges present,
this value doubles to 2\%.
With 90\% of the edges rewired,
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The rewiring scheme does not require adding any additional edges.
}
\label{fig:diameter}
\end{figure}

\begin{figure}[ht]
\centerline{\includegraphics[width=3in]{fig-mincut}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The effective redundancy is shown for several values of trust transitivity $h$.
For $h>0$, the original network has higher effective redundancy up to a crossover point,
after which the rewired network performs better.
}
\label{fig:mincut}
\end{figure}

@@

\begin{figure}[ht]

@@

\begin{figure}[ht]
\begin{center}
\includegraphics{fig-routing}
\end{center}
\caption{
An example of one path as constructed by the proposed multipath
routing algorithm.
The path is shown for $s = 10_2$
and $w = (6, 0110111_2)$.
\label{fig:routing}
}
\end{figure}

@@

\section*{Acknowledgments}
The authors would like to thank Tony Garnock-Jones, A. Frederick Dudley, and
Nathaniel Bezanson for helpful conversations.
This research was partly supported by the National Science Foundation unde;r Grant No. IIS-1617820.

\bibliographystyle{abbrv}
\bibliography{preprint}  % sigproc.bib is the name of the Bibliography in this case
\end{document}
